\begin{chapter}{Further Algorithms}
    \begin{section}{Parallel Sum}
        \par The project includes additional modules not part of the presented submissions, such as two parallel summation algorithms: \textbf{Ringsum} and \textbf{Cascadesum}.
        \par The latter is more efficient with respect to time complexity, requiring only $\log_2(P)$ steps for message passing, as opposed to $P - 1$, where $P$ denotes the number of processes involved.
    \end{section}
    \begin{section}{MatMatThread}
        \par MatMatThread is implemented with $NTROW \times NTCOL$ threads. Each thread performs a single matrix-matrix product, i.e. computes a \textbf{single block} of $\mathbf{C}$. It gives the best $\frac{N_{mem}}{N{flop}}$ ratio, $N_{mem} = \mathcal{O}(N^2)$.
        \par Another similar idea of approaching MatMatThread has been analyzed: $NTHREADS$ threads are given, each of which performs a single matrix-matrix product, i.e. computes a \textbf{single block of rows} of $\mathbf{C}$, $N_{mem} = \mathcal{O}(N^2)$.\\
        \par Other two approaches have been analyzed, too. They exhibit $N_{mem} = \mathcal{O}(N^3)$ and are:
        \begin{itemize}
            \item $NTROW \times NTCOL$ threads are given. A thread performs more vector-vector products, i.e. computes \textbf{more sparse} elements $\mathbf{C}(i,j)$.
            \item $NTHREADS$ threads are given. A thread performs more vector-matrix products, i.e. computes \textbf{more sparse} rows $\mathbf{C}(i,:)$.
        \end{itemize}
        This difference in the complexity of $N_{mem}$ that shows up is due to more main memory accesses to the same elements.
    \end{section}
    \begin{section}{MatMatDist}
        \par Another analyzed way of approaching MatMatDist is the Cannon algorithm. Despite it reaches a better efficiency $\left( E = \frac{1}{1 + \frac{\sqrt{P}}{N} \cdot \frac{N_{mem}}{N_{flop}}}\right)$ compared to \glsxtrshort{summa} $\left( E = \frac{1}{1 + \frac{\sqrt{P} \log_2{\sqrt{P}}}{N} \cdot \frac{N_{mem}}{N_{flop}}} \right)$, it can't be used for a number of processes which is not a perfect square.
    \end{section}
\end{chapter}